---
title: "PM25_Trend"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r message=FALSE}
library(ggplot2)
library(dplyr)
library(lubridate)
library(magrittr)

```

# Read and inspect the data
```{r}
pm25 <- read.table("Data_TS/PRSA_data_2010.1.1-2014.12.31.csv", sep=",", skip = 0,  header = T)
head(pm25)
tail(pm25)
```
# Preliminary EDA
```{r}
# summary(pm25)
qplot(data = pm25, x=year, y=pm2.5)
```
# Data wrangling 
* need to combined 'year', 'month', 'day', and 'hour' to build a time or date column 
Ref : https://stackoverflow.com/questions/26334763/merge-three-different-columns-into-a-date-in-r
```{r}
pm25$date <- with(pm25, paste(year, month,day,  sep="-"))
pm25$time <- with(pm25, paste(date, hour , sep=" "))
# pm25$date <- paste(pm25$year, pm25$mon, pm25$day, sep="-") %>% ymd() %>% as.Date()
pm25$time <- with(pm25, ymd_h(time))
head(pm25)
```

How many data points that are 'NA' and to sample daily average of the pm25 levels
```{r}
pm25_day <- pm25 %>% 
  na.omit() %>%
  group_by(Time= cut(time, 'days')) %>% 
  summarise(pm2.5=mean(pm2.5))

head(pm25_day)
# qplot(x=pm25_day$Time, y=pm25_day$pm2.5)
```
Plot the pm25 again, it shows the interval patterns over time
* after sampling the 'time' converted to 'factor', need to convert back to date, but first do the 'character' then 'date, it needs two steps.
```{r}
pm25_day %>% 
  ggplot(aes(x=as.Date(as.character(Time)), y=pm2.5)) +
  geom_line()+
  ylab("pm2.5 mg/m3")+
  xlab("") + 
  ggtitle("PM2.5 Trend Over Time")
# Still too many points in the plot
```


```{r}
pm25_trend <- pm25[, c("time", "pm2.5")]
```
# Data Preparation for Time Series analysis
Convert data set time series
```{r}
library(xts)
pm25_xts<-xts(pm25_trend[,-1], order.by = pm25_trend$time)
# looks like xts convert everything into 'char'
str(pm25_xts)
```
Plot the time series after conversion :
```{r}
# autoplot(pm25_xts[, "pm2.5"])
plot.ts(pm25_xts)
# autoplot(pm25_xts)
# head(pm25_xts)
```
To smooth out the pm2.5 concentration - weekly or 168 hour interval
```{r}
# add simple moving average
library("TTR")
# pm25_xts <- na.omit(pm25_xts)
# head(pm25_xts)
pm25_xts <- na.omit(pm25_xts)
# pm25_xts$pm2.5 <- as.numeric(pm25_xts$pm2.5)
```
Plot it on a 'weekly' basis, which is 168 hours equivalent
```{r}
# autoplot(pm25_xts)
pm25_xts_sma <- SMA(pm25_xts, 168) # 24 hour average, or per day
autoplot(pm25_xts_sma)
```
Make 'Difference' on data to make data stationary on mean (remove trend)
```{r}
autoplot(diff(pm25_xts),ylab='Differenced pm2.5 concentration')
```
It looks like there are still some lumps around the 'year' transition period

Plot ACF and PACF to identify potential AR and MA model
```{r fig.height=3, fig.width=8}
par(mfrow = c(1,2))
acf(na.omit(diff(pm25_xts)),main='pm25')
pacf(na.omit(diff(pm25_xts)),main='pm25')
```
```{r}
# try decompose func on the ts
decompose(pm25_xts_sma) # runs into error, no or less than 2 periods
```

Identification of best fit ARIMA model
```{r}
require(forecast)
ARIMAfit <- auto.arima(pm25_xts, approximation=FALSE,trace=FALSE)
summary(ARIMAfit)
```
Forecast pm2.5 using the best fit ARIMA model 
https://stackoverflow.com/questions/7154133/plot-new-has-not-been-called-yet
trouble shooting - run the lines together, select all lines and run ! solved
```{r}
pred.steps <- 48 # hours
par(mfrow = c(1,1))
pred <- predict(ARIMAfit, n.ahead = pred.steps)
# pred
# plot(pm25_xts,type='l', xlab = 'Hour', ylab = 'pm2.5 levels')
# lines(pred$pred,col='blue')
# lines(pred$pred+2*pred$se,col='orange')
# lines(pred$pred-2*pred$se,col='orange')

plot(x=c(1:pred.steps), y=pred$pred,col='blue')
```
Observe the ACF :
```{r message=FALSE, warning=FALSE}
library(fpp2)
ggAcf(pm25_xts) +
  ggtitle("pm2.5 concentration ACF profile")
```
To preidct the next hour pm2.5 concentration :
```{r}
ARIMAfit%>%forecast(h=72)%>%autoplot()
```
The Arima model is not that 'impressive', let's try ets model for the forecasting :
```{r}
pm25_xts%>%ets()%>% forecast(h=168) %>%autoplot()
```
```{r}
checkresiduals(ARIMAfit)
```
```{r}
# to use season arima on the pm2.5 xts
library(astsa)

```
```{r}
# try D=1, or seasonal=TRUE
sarima.fit <- auto.arima(pm25_xts, D=1, seasonal=TRUE)
summary(sarima.fit)
```
* it looks like there is no difference. it cannot tell the difference in a 'yearly' pattern; maybe too many points


