---
title: "PM25_Trend_prophet"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r message=FALSE}
library(ggplot2)
library(dplyr)
library(lubridate)
library(magrittr)

```

# Read and inspect the data
```{r}
pm25 <- read.table("PRSA_data_2010.1.1-2014.12.31.csv", sep=",", skip = 0,  header = T)
head(pm25)
tail(pm25)
```
# Preliminary EDA and Data wrangling 
* need to combined 'year', 'month', 'day', and 'hour' to build a time or date column 
Ref : https://stackoverflow.com/questions/26334763/merge-three-different-columns-into-a-date-in-r
```{r}
pm25$date <- with(pm25, paste(year, month,day,  sep="-"))
pm25$time <- with(pm25, paste(date, hour , sep=" "))
# pm25$date <- paste(pm25$year, pm25$mon, pm25$day, sep="-") %>% ymd() %>% as.Date()
pm25$time <- with(pm25, ymd_h(time))
head(pm25)
```
Check the data structure again
```{r}
str(pm25)
```
Plot a shorter time frame (before 2011)
```{r}
pm25 %>% filter(time < "2011-01-01") %>%
  ggplot(aes(x=time, y=pm2.5)) +
  geom_line()+
  ylab("pm2.5 mg/m3")+
  xlab("") + 
  ggtitle("PM2.5 Trend Over Time")
```
How many data points that are 'NA' and to sample daily average of the pm25 levels
```{r}
pm25_day <- pm25 %>% 
  na.omit() %>%
  group_by(Time= cut(time, 'days')) %>% 
  summarise(pm2.5=mean(pm2.5))

head(pm25_day)
# qplot(x=pm25_day$Time, y=pm25_day$pm2.5)
```
Plot the pm25 again, it shows the interval patterns over time
* after sampling the 'time' converted to 'factor', need to convert back to date, but first do the 'character' then 'date, it needs two steps.
```{r}
pm25_day %>% 
  ggplot(aes(x=as.Date(as.character(Time)), y=pm2.5)) +
  geom_line()+
  ylab("pm2.5 mg/m3")+
  xlab("") + 
  ggtitle("PM2.5 Trend Over Time")
# Still too many points in the plot
```

To create a dataframe with 'time' and 'pm2.5' only, two columns only
```{r}
pm25_day$Time <- as.Date(as.character(pm25_day$Time))
head(pm25_day)
# pm25_trend <- pm25[, c("time", "pm2.5")]
colnames(pm25_day) <- list('ds', 'y')
# pm25_trend <- na.omit(pm25_trend)
# head(pm25_trend)
# tail(pm25_trend)
```
Reference for the anomaly analysis package from facebook
https://facebook.github.io/prophet/docs/quick_start.html#r-api

```{r}
library(prophet)
m <- prophet(pm25_day)
```
```{r}
future <- make_future_dataframe(m, periods = 365)
tail(future)
dim(future)
```

```{r}
forecast <- predict(m, future)
tail(forecast[c('ds', 'yhat', 'yhat_lower', 'yhat_upper')])
```

```{r}
plot(m, forecast)
```
```{r}
prophet_plot_components(m, forecast)
```


