---
title: "PM25_Trend_Anomaly Detection"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r message=FALSE}
library(ggplot2)
library(dplyr)
library(lubridate)
library(magrittr)
library(tidyverse)
```

# Read and inspect the data
```{r}
pm25 <- read.table("Data_TS/PRSA_data_2010.1.1-2014.12.31.csv", sep=",", skip = 0,  header = T)
head(pm25)
tail(pm25)
```
# Preliminary EDA
```{r}
# summary(pm25)
qplot(data = pm25, x=as.factor(year), y=pm2.5, geom = "boxplot")
```
# Data wrangling 
* need to combined 'year', 'month', 'day', and 'hour' to build a time or date column 
Ref : https://stackoverflow.com/questions/26334763/merge-three-different-columns-into-a-date-in-r
```{r}
pm25$date <- with(pm25, paste(year, month,day,  sep="-"))
pm25$time <- with(pm25, paste(date, hour , sep=" "))
# pm25$date <- paste(pm25$year, pm25$mon, pm25$day, sep="-") %>% ymd() %>% as.Date()
pm25$time <- with(pm25, ymd_h(time))
head(pm25)
```
Check the data structure and plot it again 
```{r}
str(pm25)

```
Plot pm2.5 levels over time frame (year by year)
```{r fig.height=10, message=FALSE}
pm25 %>% ggplot(aes(x=time, y=pm2.5)) +
  geom_line()+
  ylab("pm2.5 mg/m3")+
  xlab("") + 
  ylim(0, 1000)+
  ggtitle("PM2.5 Trend Over Time")+
  facet_wrap(~ year, nrow = 5, scales="free")
```
How many data points that are 'NA' and to sample daily average of the pm25 levels
```{r}
pm25_day <- pm25 %>% 
  na.omit() %>%
  group_by(Time= cut(time, 'days')) %>% 
  summarise(pm2.5=mean(pm2.5))
  
```
Plot the pm25 again, it shows the interval patterns over time (daily)
* after sampling the 'time' converted to 'factor', need to convert back to date, but first do the 'character' then 'date, it needs two steps.
```{r fig.height=10}
pm25_day$Time <- as.Date(as.character(pm25_day$Time))
pm25_day %>% ggplot(aes(x=Time, y=pm2.5)) +
  geom_line()+
  ylab("pm2.5 mg/m3")+
  xlab("") + 
  ylim(0, 500) +
  ggtitle("PM2.5 Trend Over Time")+
  facet_wrap(~ year(Time), nrow = 5, scales="free") # use 'lubricate' to extract year
```


```{r}
pm25_trend <- pm25[, c("time", "pm2.5")]
```
```{r}
# check the data structure again
str(pm25_trend)
sum(is.na(pm25_trend))
pm25_trend <- na.omit(pm25_trend)

# check NAs again 
sum(is.na(pm25_trend))
```
Apply anomaly function 
Reference : https://www.r-bloggers.com/anomaly-detection-in-r-2/
```{r}
#Install the devtools package then github packages
# install.packages("devtools")
# install.packages("Rcpp")
library(devtools)
# install_github("petermeissner/wikipediatrend")
# install_github("twitter/AnomalyDetection")
library(AnomalyDetection)

anomalies_pm25 <- AnomalyDetectionTs(pm25_trend, direction="pos", plot=TRUE)
anomalies_pm25$plot
```
```{r}
# number of anomaly points
nrow(anomalies_pm25$anoms)

# create a lable for outliers
pm25_trend$outliers <- ifelse(pm25_trend$time %in% anomalies_pm25$anoms$timestamp, 1, 0)
head(pm25_trend)
```

```{r}
plot(pm25_trend$outliers) # not good result
class(pm25_trend$time)
class(anomalies_pm25$anoms$timestamp)
```
```{r}
anomlies_points <- data.frame(time=anomalies_pm25$anoms$timestamp, 
                              pm2.5=anomalies_pm25$anoms$anoms)

head(anomlies_points)
str(anomlies_points)
pm25_trend2 <- pm25_trend %>% left_join(anomlies_points, by='time')
head(pm25_trend2)
pm25_trend2$outliers <- ifelse(is.na(pm25_trend2$pm2.5.y), 0, 1)  

```
Plot the trend again over the years with 'labled' outliers
```{r fig.height=10, message=FALSE}
pm25_trend2 %>% ggplot(aes(x=time, y=pm2.5.x)) +
  geom_line()+
  geom_point(aes(x=time, y=pm2.5.x, col=as.factor(outliers)), size=0.5) +
  ylab("pm2.5 mg/m3")+
  xlab("") + 
  ylim(0, 1000)+
  ggtitle("PM2.5 Trend Over Time")+
  facet_wrap(~ year(time), nrow = 5, scales="free")
```
# Use AnomalyDetectionVec
```{r}
pm25_ad <- AnomalyDetectionVec(x=pm25_trend$pm2.5, period = 8760, direction = 'both', plot=T)
pm25_ad$plot
```
# number of amomaly points
```{r}
nrow(pm25_ad$anoms)
head(pm25_ad$anoms)
nrow(pm25_ad$anoms)/nrow(pm25_trend) # same as on the plot
```
# it looks like from October to March next year, every year, during which the 'unsual' spikes of the pm25 levels are most likely to happen.

