---
title: "sunspot_lstm_keras"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The codes and data are from :
https://www.business-science.io/timeseries-analysis/2018/04/18/keras-lstm-sunspots-time-series-prediction.html
** certain descriptions are shortened to be brief on the subject

## 1.0 Libraries
```{r message=FALSE, warning=FALSE}
# Core Tidyverse
library(tidyverse)
library(glue)
library(forcats)

# Time Series
library(timetk)
library(tidyquant)
library(tibbletime)

# Visualization
library(cowplot)

# Preprocessing
library(recipes)

# Sampling / Accuracy
library(rsample)
library(yardstick) 

# Modeling
library(keras)
```
### 2.0 Data

```{r}
# The dataset, sunspot.month, is available for all of us (it ships with base R). It's a ts class (not tidy), so we'll convert to a tidy 
# data set using the tk_tbl() function from timetk. We use this instead of as.tibble() from tibble to automatically preserve the time 
# series index as a zoo yearmon index. Last, we'll convert the zoo index to date using lubridate::as_date() (loaded with tidyquant) and
# then change to a tbl_time object to make time series operations easier.
sun_spots <- datasets::sunspot.month %>%
    tk_tbl() %>%
    mutate(index = as_date(index)) %>%
    as_tbl_time(index = index)

sun_spots
```
## 3.0 Exploratory Data Analysis
### 3.1 Visualizing Sunspot Data With Cowplot
```{r}
p1 <- sun_spots %>%
    ggplot(aes(index, value)) +
    geom_point(color = palette_light()[[1]], alpha = 0.5) +
    theme_tq() +
    labs(title = "From 1749 to 2013 (Full Data Set)")

p2 <- sun_spots %>%
    filter_time("start" ~ "1800") %>%
    ggplot(aes(index, value)) +
    geom_line(color = palette_light()[[1]], alpha = 0.5) +
    geom_point(color = palette_light()[[1]]) +
    geom_smooth(method = "loess", span = 0.2, se = FALSE) +
    theme_tq() +
    labs(title = "1749 to 1800 (Zoomed In To Show Cycle)",
        caption = "datasets::sunspot.month")

p_title <- ggdraw() + 
    draw_label("Sunspots", size = 18, fontface = "bold", colour = palette_light()[[1]])

plot_grid(p_title, p1, p2, ncol = 1, rel_heights = c(0.1, 1, 1))
```
### 3.2 Evaluating The ACF
```{r}

#  To do so, we'll create a custom function, tidy_acf(), to return the ACF values in a tidy tibble.

tidy_acf <- function(data, value, lags = 0:20) {
    
    value_expr <- enquo(value)
    
    acf_values <- data %>%
        pull(value) %>%
        acf(lag.max = tail(lags, 1), plot = FALSE) %>%
        .$acf %>%
        .[,,1]
    
    ret <- tibble(acf = acf_values) %>%
        rowid_to_column(var = "lag") %>%
        mutate(lag = lag - 1) %>%
        filter(lag %in% lags)
    
    return(ret)
}
```

```{r}
# The function takes our tidy time series, extracts the value column, and returns the ACF values along with the associated lag in a tibble format.
max_lag <- 12 * 50

sun_spots %>%
    tidy_acf(value, lags = 0:max_lag)
```
```{r}
# plot the ACF with ggplot2 to determine if a high-autocorrelation lag exists beyond 10 years.
sun_spots %>%
    tidy_acf(value, lags = 0:max_lag) %>%
    ggplot(aes(lag, acf)) +
    geom_segment(aes(xend = lag, yend = 0), color = palette_light()[[1]]) +
    geom_vline(xintercept = 120, size = 3, color = palette_light()[[2]]) +
    annotate("text", label = "10 Year Mark", x = 130, y = 0.8, 
             color = palette_light()[[2]], size = 6, hjust = 0) +
    theme_tq() +
    labs(title = "ACF: Sunspots")
```

```{r}
# We have autocorrelation in excess of 0.5 beyond lag 120 (the 10-year mark). 
sun_spots %>%
    tidy_acf(value, lags = 115:135) %>%
    ggplot(aes(lag, acf)) +
    geom_vline(xintercept = 120, size = 3, color = palette_light()[[2]]) +
    geom_segment(aes(xend = lag, yend = 0), color = palette_light()[[1]]) +
    geom_point(color = palette_light()[[1]], size = 2) +
    geom_label(aes(label = acf %>% round(2)), vjust = -1,
              color = palette_light()[[1]]) +
    annotate("text", label = "10 Year Mark", x = 121, y = 0.8, 
             color = palette_light()[[2]], size = 5, hjust = 0) +
    theme_tq() +
    labs(title = "ACF: Sunspots",
         subtitle = "Zoomed in on Lags 115 to 135")
```
```{r}
# you can filter() to get the best lag.
optimal_lag_setting <- sun_spots %>%
    tidy_acf(value, lags = 115:135) %>%
    filter(acf == max(acf)) %>%
    pull(lag)

optimal_lag_setting
```
## 4.0 Backtesting: Time Series Cross Validation
### 4.1 Developing A Backtesting Strategy
```{r}
periods_train <- 12 * 50
periods_test  <- 12 * 10
skip_span     <- 12 * 20

rolling_origin_resamples <- rolling_origin(
    sun_spots,
    initial    = periods_train,
    assess     = periods_test,
    cumulative = FALSE,
    skip       = skip_span
)

rolling_origin_resamples
```
### 4.2 Visualizing The Backtesting Strategy
```{r}
# Plotting function for a single split
plot_split <- function(split, expand_y_axis = TRUE, alpha = 1, size = 1, base_size = 14) {
    
    # Manipulate data
    train_tbl <- training(split) %>%
        add_column(key = "training") 
    
    test_tbl  <- testing(split) %>%
        add_column(key = "testing") 
    
    data_manipulated <- bind_rows(train_tbl, test_tbl) %>%
        as_tbl_time(index = index) %>%
        mutate(key = fct_relevel(key, "training", "testing"))
        
    # Collect attributes
    train_time_summary <- train_tbl %>%
        tk_index() %>%
        tk_get_timeseries_summary()
    
    test_time_summary <- test_tbl %>%
        tk_index() %>%
        tk_get_timeseries_summary()
    
    # Visualize
    g <- data_manipulated %>%
        ggplot(aes(x = index, y = value, color = key)) +
        geom_line(size = size, alpha = alpha) +
        theme_tq(base_size = base_size) +
        scale_color_tq() +
        labs(
            title    = glue("Split: {split$id}"),
            subtitle = glue("{train_time_summary$start} to {test_time_summary$end}"),
            y = "", x = ""
        ) +
        theme(legend.position = "none") 
    
    if (expand_y_axis) {
        
        sun_spots_time_summary <- sun_spots %>% 
            tk_index() %>% 
            tk_get_timeseries_summary()
        
        g <- g +
            scale_x_date(limits = c(sun_spots_time_summary$start, 
                                    sun_spots_time_summary$end))
    }
    
    return(g)
}
```
```{r}
rolling_origin_resamples$splits[[1]] %>%
    plot_split(expand_y_axis = TRUE) +
    theme(legend.position = "bottom")
```
```{r}
# The second function, plot_sampling_plan(), scales the plot_split() function to all of the samples using purrr and cowplot.

# Plotting function that scales to all splits 
plot_sampling_plan <- function(sampling_tbl, expand_y_axis = TRUE, 
                               ncol = 3, alpha = 1, size = 1, base_size = 14, 
                               title = "Sampling Plan") {
    
    # Map plot_split() to sampling_tbl
    sampling_tbl_with_plots <- sampling_tbl %>%
        mutate(gg_plots = map(splits, plot_split, 
                              expand_y_axis = expand_y_axis,
                              alpha = alpha, base_size = base_size))
    
    # Make plots with cowplot
    plot_list <- sampling_tbl_with_plots$gg_plots 
    
    p_temp <- plot_list[[1]] + theme(legend.position = "bottom")
    legend <- get_legend(p_temp)
    
    p_body  <- plot_grid(plotlist = plot_list, ncol = ncol)
    
    p_title <- ggdraw() + 
        draw_label(title, size = 18, fontface = "bold", colour = palette_light()[[1]])
    
    g <- plot_grid(p_title, p_body, legend, ncol = 1, rel_heights = c(0.05, 1, 0.05))
    
    return(g)
    
}
```
```{r, fig.height=10, fig.width=8}
# We can see how the sampling plan shifts the sampling window with each progressive slice of the train/test splits.
rolling_origin_resamples %>%
    plot_sampling_plan(expand_y_axis = T, ncol = 3, alpha = 1, size = 1, base_size = 10, 
                       title = "Backtesting Strategy: Rolling Origin Sampling Plan")
```
```{r fig.height=10, fig.width=8, message=FALSE, warning=FALSE}
# And, we can set expand_y_axis = FALSE to zoom in on the samples.
rolling_origin_resamples %>%
    plot_sampling_plan(expand_y_axis = F, ncol = 3, alpha = 1, size = 1, base_size = 10, 
                       title = "Backtesting Strategy: Zoomed In")
```
* We'll use this Backtesting Strategy (11 samples from one time series each with 50/10 split in years and a 20 year offset) when testing the veracity of the LSTM model on the sunspots dataset.

