---
title: "sunspot_lstm_keras"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The codes and data are from :
https://www.business-science.io/timeseries-analysis/2018/04/18/keras-lstm-sunspots-time-series-prediction.html
** certain descriptions are shortened to be brief on the subject

## 1.0 Libraries
```{r message=FALSE, warning=FALSE}
# Core Tidyverse
library(tidyverse)
library(glue)
library(forcats)

# Time Series
library(timetk)
library(tidyquant)
library(tibbletime)

# Visualization
library(cowplot)

# Preprocessing
library(recipes)

# Sampling / Accuracy
library(rsample)
library(yardstick) 

# Modeling
library(keras)
```
### 2.0 Data

```{r}
# The dataset, sunspot.month, is available for all of us (it ships with base R). It's a ts class (not tidy), so we'll convert to a tidy 
# data set using the tk_tbl() function from timetk. We use this instead of as.tibble() from tibble to automatically preserve the time 
# series index as a zoo yearmon index. Last, we'll convert the zoo index to date using lubridate::as_date() (loaded with tidyquant) and
# then change to a tbl_time object to make time series operations easier.
sun_spots <- datasets::sunspot.month %>%
    tk_tbl() %>%
    mutate(index = as_date(index)) %>%
    as_tbl_time(index = index)

sun_spots
```
## 3.0 Exploratory Data Analysis
### 3.1 Visualizing Sunspot Data With Cowplot
```{r}
p1 <- sun_spots %>%
    ggplot(aes(index, value)) +
    geom_point(color = palette_light()[[1]], alpha = 0.5) +
    theme_tq() +
    labs(title = "From 1749 to 2013 (Full Data Set)")

p2 <- sun_spots %>%
    filter_time("start" ~ "1800") %>%
    ggplot(aes(index, value)) +
    geom_line(color = palette_light()[[1]], alpha = 0.5) +
    geom_point(color = palette_light()[[1]]) +
    geom_smooth(method = "loess", span = 0.2, se = FALSE) +
    theme_tq() +
    labs(title = "1749 to 1800 (Zoomed In To Show Cycle)",
        caption = "datasets::sunspot.month")

p_title <- ggdraw() + 
    draw_label("Sunspots", size = 18, fontface = "bold", colour = palette_light()[[1]])

plot_grid(p_title, p1, p2, ncol = 1, rel_heights = c(0.1, 1, 1))
```
### 3.2 Evaluating The ACF
```{r}

#  To do so, we'll create a custom function, tidy_acf(), to return the ACF values in a tidy tibble.

tidy_acf <- function(data, value, lags = 0:20) {
    
    value_expr <- enquo(value)
    
    acf_values <- data %>%
        pull(value) %>%
        acf(lag.max = tail(lags, 1), plot = FALSE) %>%
        .$acf %>%
        .[,,1]
    
    ret <- tibble(acf = acf_values) %>%
        rowid_to_column(var = "lag") %>%
        mutate(lag = lag - 1) %>%
        filter(lag %in% lags)
    
    return(ret)
}
```

```{r}
# The function takes our tidy time series, extracts the value column, and returns the ACF values along with the associated lag in a tibble format.
max_lag <- 12 * 50

sun_spots %>%
    tidy_acf(value, lags = 0:max_lag)
```
```{r}
# plot the ACF with ggplot2 to determine if a high-autocorrelation lag exists beyond 10 years.
sun_spots %>%
    tidy_acf(value, lags = 0:max_lag) %>%
    ggplot(aes(lag, acf)) +
    geom_segment(aes(xend = lag, yend = 0), color = palette_light()[[1]]) +
    geom_vline(xintercept = 120, size = 3, color = palette_light()[[2]]) +
    annotate("text", label = "10 Year Mark", x = 130, y = 0.8, 
             color = palette_light()[[2]], size = 6, hjust = 0) +
    theme_tq() +
    labs(title = "ACF: Sunspots")
```

```{r}
# We have autocorrelation in excess of 0.5 beyond lag 120 (the 10-year mark). 
sun_spots %>%
    tidy_acf(value, lags = 115:135) %>%
    ggplot(aes(lag, acf)) +
    geom_vline(xintercept = 120, size = 3, color = palette_light()[[2]]) +
    geom_segment(aes(xend = lag, yend = 0), color = palette_light()[[1]]) +
    geom_point(color = palette_light()[[1]], size = 2) +
    geom_label(aes(label = acf %>% round(2)), vjust = -1,
              color = palette_light()[[1]]) +
    annotate("text", label = "10 Year Mark", x = 121, y = 0.8, 
             color = palette_light()[[2]], size = 5, hjust = 0) +
    theme_tq() +
    labs(title = "ACF: Sunspots",
         subtitle = "Zoomed in on Lags 115 to 135")
```
```{r}
# you can filter() to get the best lag.
optimal_lag_setting <- sun_spots %>%
    tidy_acf(value, lags = 115:135) %>%
    filter(acf == max(acf)) %>%
    pull(lag)

optimal_lag_setting
```
## 4.0 Backtesting: Time Series Cross Validation
### 4.1 Developing A Backtesting Strategy
```{r}
periods_train <- 12 * 50
periods_test  <- 12 * 10
skip_span     <- 12 * 20

rolling_origin_resamples <- rolling_origin(
    sun_spots,
    initial    = periods_train,
    assess     = periods_test,
    cumulative = FALSE,
    skip       = skip_span
)

rolling_origin_resamples
```
### 4.2 Visualizing The Backtesting Strategy
```{r}
# Plotting function for a single split
plot_split <- function(split, expand_y_axis = TRUE, alpha = 1, size = 1, base_size = 14) {
    
    # Manipulate data
    train_tbl <- training(split) %>%
        add_column(key = "training") 
    
    test_tbl  <- testing(split) %>%
        add_column(key = "testing") 
    
    data_manipulated <- bind_rows(train_tbl, test_tbl) %>%
        as_tbl_time(index = index) %>%
        mutate(key = fct_relevel(key, "training", "testing"))
        
    # Collect attributes
    train_time_summary <- train_tbl %>%
        tk_index() %>%
        tk_get_timeseries_summary()
    
    test_time_summary <- test_tbl %>%
        tk_index() %>%
        tk_get_timeseries_summary()
    
    # Visualize
    g <- data_manipulated %>%
        ggplot(aes(x = index, y = value, color = key)) +
        geom_line(size = size, alpha = alpha) +
        theme_tq(base_size = base_size) +
        scale_color_tq() +
        labs(
            title    = glue("Split: {split$id}"),
            subtitle = glue("{train_time_summary$start} to {test_time_summary$end}"),
            y = "", x = ""
        ) +
        theme(legend.position = "none") 
    
    if (expand_y_axis) {
        
        sun_spots_time_summary <- sun_spots %>% 
            tk_index() %>% 
            tk_get_timeseries_summary()
        
        g <- g +
            scale_x_date(limits = c(sun_spots_time_summary$start, 
                                    sun_spots_time_summary$end))
    }
    
    return(g)
}
```
```{r}
rolling_origin_resamples$splits[[1]] %>%
    plot_split(expand_y_axis = TRUE) +
    theme(legend.position = "bottom")
```
```{r}
# The second function, plot_sampling_plan(), scales the plot_split() function to all of the samples using purrr and cowplot.

# Plotting function that scales to all splits 
plot_sampling_plan <- function(sampling_tbl, expand_y_axis = TRUE, 
                               ncol = 3, alpha = 1, size = 1, base_size = 14, 
                               title = "Sampling Plan") {
    
    # Map plot_split() to sampling_tbl
    sampling_tbl_with_plots <- sampling_tbl %>%
        mutate(gg_plots = map(splits, plot_split, 
                              expand_y_axis = expand_y_axis,
                              alpha = alpha, base_size = base_size))
    
    # Make plots with cowplot
    plot_list <- sampling_tbl_with_plots$gg_plots 
    
    p_temp <- plot_list[[1]] + theme(legend.position = "bottom")
    legend <- get_legend(p_temp)
    
    p_body  <- plot_grid(plotlist = plot_list, ncol = ncol)
    
    p_title <- ggdraw() + 
        draw_label(title, size = 18, fontface = "bold", colour = palette_light()[[1]])
    
    g <- plot_grid(p_title, p_body, legend, ncol = 1, rel_heights = c(0.05, 1, 0.05))
    
    return(g)
    
}
```
```{r, fig.height=10, fig.width=8}
# We can see how the sampling plan shifts the sampling window with each progressive slice of the train/test splits.
rolling_origin_resamples %>%
    plot_sampling_plan(expand_y_axis = T, ncol = 3, alpha = 1, size = 1, base_size = 10, 
                       title = "Backtesting Strategy: Rolling Origin Sampling Plan")
```
```{r fig.height=10, fig.width=8, message=FALSE, warning=FALSE}
# And, we can set expand_y_axis = FALSE to zoom in on the samples.
rolling_origin_resamples %>%
    plot_sampling_plan(expand_y_axis = F, ncol = 3, alpha = 1, size = 1, base_size = 10, 
                       title = "Backtesting Strategy: Zoomed In")
```
* We'll use this Backtesting Strategy (11 samples from one time series each with 50/10 split in years and a 20 year offset) when testing the veracity of the LSTM model on the sunspots dataset.

# 5.0 Modeling The Keras Stateful LSTM Model
## 5.1 Single LSTM
```{r}
split    <- rolling_origin_resamples$splits[[11]]
split_id <- rolling_origin_resamples$id[[11]]
```
```{r}
# 5.1.1 Visualizing The Split
plot_split(split, expand_y_axis = FALSE, size = 0.5) +
    theme(legend.position = "bottom") +
    ggtitle(glue("Split: {split_id}"))
```
```{r}
# 5.1.2 Data Setup
df_trn <- training(split)
df_tst <- testing(split)

df <- bind_rows(
    df_trn %>% add_column(key = "training"),
    df_tst %>% add_column(key = "testing")
) %>% 
    as_tbl_time(index = index)

df
```
```{r}
# 5.1.3 Preprocessing With Recipes
rec_obj <- recipe(value ~ ., df) %>%
    step_sqrt(value) %>%
    step_center(value) %>%
    step_scale(value) %>%
    prep()

df_processed_tbl <- bake(rec_obj, df)

df_processed_tbl
```
```{r}
center_history <- rec_obj$steps[[2]]$means["value"]
scale_history  <- rec_obj$steps[[3]]$sds["value"]

c("center" = center_history, "scale" = scale_history)
```
```{r}
# 5.1.4 LSTM Plan
# Model inputs
lag_setting  <- 120 # = nrow(df_tst)
batch_size   <- 40
train_length <- 440
tsteps       <- 1
epochs       <- 300
```
```{r}
# 5.1.5 2D And 3D Train/Test Arrays
# Training Set
lag_train_tbl <- df_processed_tbl %>%
    mutate(value_lag = lag(value, n = lag_setting)) %>%
    filter(!is.na(value_lag)) %>%
    filter(key == "training") %>%
    tail(train_length)

x_train_vec <- lag_train_tbl$value_lag
x_train_arr <- array(data = x_train_vec, dim = c(length(x_train_vec), 1, 1))

y_train_vec <- lag_train_tbl$value
y_train_arr <- array(data = y_train_vec, dim = c(length(y_train_vec), 1))

# Testing Set
lag_test_tbl <- df_processed_tbl %>%
    mutate(
        value_lag = lag(value, n = lag_setting)
    ) %>%
    filter(!is.na(value_lag)) %>%
    filter(key == "testing")

x_test_vec <- lag_test_tbl$value_lag
x_test_arr <- array(data = x_test_vec, dim = c(length(x_test_vec), 1, 1))

y_test_vec <- lag_test_tbl$value
y_test_arr <- array(data = y_test_vec, dim = c(length(y_test_vec), 1))
```
```{r}
# 5.1.6 Building The LSTM Model
model <- keras_model_sequential()

model %>%
    layer_lstm(units            = 50, 
               input_shape      = c(tsteps, 1), 
               batch_size       = batch_size,
               return_sequences = TRUE, 
               stateful         = TRUE) %>% 
    layer_lstm(units            = 50, 
               return_sequences = FALSE, 
               stateful         = TRUE) %>% 
    layer_dense(units = 1)

model %>% 
    compile(loss = 'mae', optimizer = 'adam')

model
```
```{r}
# 5.1.7 Fitting The LSTM Model
for (i in 1:epochs) {
    model %>% fit(x          = x_train_arr, 
                  y          = y_train_arr, 
                  batch_size = batch_size,
                  epochs     = 1, 
                  verbose    = 0, 
                  shuffle    = FALSE)
    
    model %>% reset_states()
    cat("Epoch: ", i)
    
}
```
```{r}
# 5.1.8 Predicting Using The LSTM Model
# Make Predictions
pred_out <- model %>% 
    predict(x_test_arr, batch_size = batch_size) %>%
    .[,1] 

# Retransform values
pred_tbl <- tibble(
    index   = lag_test_tbl$index,
    value   = (pred_out * scale_history + center_history)^2
) 

# Combine actual data with predictions
tbl_1 <- df_trn %>%
    add_column(key = "actual")

tbl_2 <- df_tst %>%
    add_column(key = "actual")

tbl_3 <- pred_tbl %>%
    add_column(key = "predict")

# Create time_bind_rows() to solve dplyr issue
time_bind_rows <- function(data_1, data_2, index) {
    index_expr <- enquo(index)
    bind_rows(data_1, data_2) %>%
        as_tbl_time(index = !! index_expr)
}

ret <- list(tbl_1, tbl_2, tbl_3) %>%
    reduce(time_bind_rows, index = index) %>%
    arrange(key, index) %>%
    mutate(key = as_factor(key))

ret
```
```{r}
# 5.1.9 Assessing Performance Of The LSTM On A Single Split
calc_rmse <- function(prediction_tbl) {
    
    rmse_calculation <- function(data) {
        data %>%
            spread(key = key, value = value) %>%
            select(-index) %>%
            filter(!is.na(predict)) %>%
            rename(
                truth    = actual,
                estimate = predict
            ) %>%
            rmse(truth, estimate)
    }
    
    safe_rmse <- possibly(rmse_calculation, otherwise = NA)
    
    safe_rmse(prediction_tbl)
        
}
```
```{r}
# 5.1.10 Visualizing The Single Prediction
# Setup single plot function
plot_prediction <- function(data, id, alpha = 1, size = 2, base_size = 14) {
    
    rmse_val <- calc_rmse(data)
    
    g <- data %>%
        ggplot(aes(index, value, color = key)) +
        geom_point(alpha = alpha, size = size) + 
        theme_tq(base_size = base_size) +
        scale_color_tq() +
        theme(legend.position = "none") +
        labs(
            title = glue("{id}, RMSE: {round(rmse_val, digits = 1)}"),
            x = "", y = ""
        )
    
    return(g)
}
```
```{r}
# We can test out the plotting function setting the id = split_id, which is "Slice11".

ret %>% 
    plot_prediction(id = split_id, alpha = 0.65) +
    theme(legend.position = "bottom")
```
## 5.2 Backtesting The LSTM On All Eleven Samples
### 5.2.1 Creating An LSTM Prediction Function
```{r}
predict_keras_lstm <- function(split, epochs = 300, ...) {
    
    lstm_prediction <- function(split, epochs, ...) {
        
        # 5.1.2 Data Setup
        df_trn <- training(split)
        df_tst <- testing(split)
        
        df <- bind_rows(
            df_trn %>% add_column(key = "training"),
            df_tst %>% add_column(key = "testing")
        ) %>% 
            as_tbl_time(index = index)
        
        # 5.1.3 Preprocessing
        rec_obj <- recipe(value ~ ., df) %>%
            step_sqrt(value) %>%
            step_center(value) %>%
            step_scale(value) %>%
            prep()
        
        df_processed_tbl <- bake(rec_obj, df)
        
        center_history <- rec_obj$steps[[2]]$means["value"]
        scale_history  <- rec_obj$steps[[3]]$sds["value"]
        
        # 5.1.4 LSTM Plan
        lag_setting  <- 120 # = nrow(df_tst)
        batch_size   <- 40
        train_length <- 440
        tsteps       <- 1
        epochs       <- epochs
        
        # 5.1.5 Train/Test Setup
        lag_train_tbl <- df_processed_tbl %>%
            mutate(value_lag = lag(value, n = lag_setting)) %>%
            filter(!is.na(value_lag)) %>%
            filter(key == "training") %>%
            tail(train_length)
        
        x_train_vec <- lag_train_tbl$value_lag
        x_train_arr <- array(data = x_train_vec, dim = c(length(x_train_vec), 1, 1))
        
        y_train_vec <- lag_train_tbl$value
        y_train_arr <- array(data = y_train_vec, dim = c(length(y_train_vec), 1))
        
        lag_test_tbl <- df_processed_tbl %>%
            mutate(
                value_lag = lag(value, n = lag_setting)
            ) %>%
            filter(!is.na(value_lag)) %>%
            filter(key == "testing")
        
        x_test_vec <- lag_test_tbl$value_lag
        x_test_arr <- array(data = x_test_vec, dim = c(length(x_test_vec), 1, 1))
        
        y_test_vec <- lag_test_tbl$value
        y_test_arr <- array(data = y_test_vec, dim = c(length(y_test_vec), 1))
                
        # 5.1.6 LSTM Model
        model <- keras_model_sequential()

        model %>%
            layer_lstm(units            = 50, 
                       input_shape      = c(tsteps, 1), 
                       batch_size       = batch_size,
                       return_sequences = TRUE, 
                       stateful         = TRUE) %>% 
            layer_lstm(units            = 50, 
                       return_sequences = FALSE, 
                       stateful         = TRUE) %>% 
            layer_dense(units = 1)
        
        model %>% 
            compile(loss = 'mae', optimizer = 'adam')
        
        # 5.1.7 Fitting LSTM
        for (i in 1:epochs) {
            model %>% fit(x          = x_train_arr, 
                          y          = y_train_arr, 
                          batch_size = batch_size,
                          epochs     = 1, 
                          verbose    = 0, 
                          shuffle    = FALSE)
            
            model %>% reset_states()
            cat("Epoch: ", i)
            
        }
        
        # 5.1.8 Predict and Return Tidy Data
        # Make Predictions
        pred_out <- model %>% 
            predict(x_test_arr, batch_size = batch_size) %>%
            .[,1] 
        
        # Retransform values
        pred_tbl <- tibble(
            index   = lag_test_tbl$index,
            value   = (pred_out * scale_history + center_history)^2
        ) 
        
        # Combine actual data with predictions
        tbl_1 <- df_trn %>%
            add_column(key = "actual")
        
        tbl_2 <- df_tst %>%
            add_column(key = "actual")
        
        tbl_3 <- pred_tbl %>%
            add_column(key = "predict")
        
        # Create time_bind_rows() to solve dplyr issue
        time_bind_rows <- function(data_1, data_2, index) {
            index_expr <- enquo(index)
            bind_rows(data_1, data_2) %>%
                as_tbl_time(index = !! index_expr)
        }
        
        ret <- list(tbl_1, tbl_2, tbl_3) %>%
            reduce(time_bind_rows, index = index) %>%
            arrange(key, index) %>%
            mutate(key = as_factor(key))

        return(ret)
        
    }
    
    safe_lstm <- possibly(lstm_prediction, otherwise = NA)
    
    safe_lstm(split, epochs, ...)
    
}
```
* We can test the custom predict_keras_lstm() function out with 10 epochs. 
```{r}
predict_keras_lstm(split, epochs = 10)
```
### 5.2.2 Mapping The LSTM Prediction Function Over The 11 Samples
```{r}
# With the predict_keras_lstm() function in hand that works on one split, we can now map to all samples using a mutate() and map() combo. The predictions will be stored in a "list" column called "predict".
sample_predictions_lstm_tbl <- rolling_origin_resamples %>%
     mutate(predict = map(splits, predict_keras_lstm, epochs = 300))
```
* We now have the predictions in the column "predict" for all 11 splits!.
```{r}
sample_predictions_lstm_tbl
```
### 5.2.3 Assessing The Backtested Performance
* this part does not work as what blog showed; need further attention
```{r}
# We can assess the RMSE by mapping the calc_rmse() function to the "predict" column.
sample_rmse_tbl <- sample_predictions_lstm_tbl %>%
    mutate(rmse = map_dbl(predict, calc_rmse)) %>%
    select(id, rmse)

sample_rmse_tbl
```
```{r}
sample_rmse_tbl %>%
    ggplot(aes(rmse)) +
    geom_histogram(aes(y = ..density..), fill = palette_light()[[1]], bins = 16) +
    geom_density(fill = palette_light()[[1]], alpha = 0.5) +
    theme_tq() +
    ggtitle("Histogram of RMSE")
```
```{r}
sample_rmse_tbl %>%
    summarize(
        mean_rmse = mean(rmse),
        sd_rmse   = sd(rmse)
    )
```
### 5.2.4 Visualizing The Backtest Results
```{r}
plot_predictions <- function(sampling_tbl, predictions_col, 
                             ncol = 3, alpha = 1, size = 2, base_size = 14,
                             title = "Backtested Predictions") {
    
    predictions_col_expr <- enquo(predictions_col)
    
    # Map plot_split() to sampling_tbl
    sampling_tbl_with_plots <- sampling_tbl %>%
        mutate(gg_plots = map2(!! predictions_col_expr, id, 
                               .f        = plot_prediction, 
                               alpha     = alpha, 
                               size      = size, 
                               base_size = base_size)) 
    
    # Make plots with cowplot
    plot_list <- sampling_tbl_with_plots$gg_plots 
    
    p_temp <- plot_list[[1]] + theme(legend.position = "bottom")
    legend <- get_legend(p_temp)
    
    p_body  <- plot_grid(plotlist = plot_list, ncol = ncol)
    
    
    
    p_title <- ggdraw() + 
        draw_label(title, size = 18, fontface = "bold", colour = palette_light()[[1]])
    
    g <- plot_grid(p_title, p_body, legend, ncol = 1, rel_heights = c(0.05, 1, 0.05))
    
    return(g)
    
}
```
```{r}
sample_predictions_lstm_tbl %>%
    plot_predictions(predictions_col = predict, alpha = 0.5, size = 1, base_size = 10,
                     title = "Keras Stateful LSTM: Backtested Predictions")
```
## 5.3 Predicting The Next 10 Years
```{r}
# We can predict the next 10 years by adjusting the prediction function to work with the full data set. 
predict_keras_lstm_future <- function(data, epochs = 300, ...) {
    
    lstm_prediction <- function(data, epochs, ...) {
        
        # 5.1.2 Data Setup (MODIFIED)
        df <- data
        
        # 5.1.3 Preprocessing
        rec_obj <- recipe(value ~ ., df) %>%
            step_sqrt(value) %>%
            step_center(value) %>%
            step_scale(value) %>%
            prep()
        
        df_processed_tbl <- bake(rec_obj, df)
        
        center_history <- rec_obj$steps[[2]]$means["value"]
        scale_history  <- rec_obj$steps[[3]]$sds["value"]
        
        # 5.1.4 LSTM Plan
        lag_setting  <- 120 # = nrow(df_tst)
        batch_size   <- 40
        train_length <- 440
        tsteps       <- 1
        epochs       <- epochs
        
        # 5.1.5 Train Setup (MODIFIED)
        lag_train_tbl <- df_processed_tbl %>%
            mutate(value_lag = lag(value, n = lag_setting)) %>%
            filter(!is.na(value_lag)) %>%
            tail(train_length)
        
        x_train_vec <- lag_train_tbl$value_lag
        x_train_arr <- array(data = x_train_vec, dim = c(length(x_train_vec), 1, 1))
        
        y_train_vec <- lag_train_tbl$value
        y_train_arr <- array(data = y_train_vec, dim = c(length(y_train_vec), 1))
        
        x_test_vec <- y_train_vec %>% tail(lag_setting)
        x_test_arr <- array(data = x_test_vec, dim = c(length(x_test_vec), 1, 1))
                
        # 5.1.6 LSTM Model
        model <- keras_model_sequential()

        model %>%
            layer_lstm(units            = 50, 
                       input_shape      = c(tsteps, 1), 
                       batch_size       = batch_size,
                       return_sequences = TRUE, 
                       stateful         = TRUE) %>% 
            layer_lstm(units            = 50, 
                       return_sequences = FALSE, 
                       stateful         = TRUE) %>% 
            layer_dense(units = 1)
        
        model %>% 
            compile(loss = 'mae', optimizer = 'adam')
        
        # 5.1.7 Fitting LSTM
        for (i in 1:epochs) {
            model %>% fit(x          = x_train_arr, 
                          y          = y_train_arr, 
                          batch_size = batch_size,
                          epochs     = 1, 
                          verbose    = 1, 
                          shuffle    = FALSE)
            
            model %>% reset_states()
            cat("Epoch: ", i)
            
        }
        
        # 5.1.8 Predict and Return Tidy Data (MODIFIED)
        # Make Predictions
        pred_out <- model %>% 
            predict(x_test_arr, batch_size = batch_size) %>%
            .[,1] 
        
        # Make future index using tk_make_future_timeseries()
        idx <- data %>%
            tk_index() %>%
            tk_make_future_timeseries(n_future = lag_setting)
        
        # Retransform values
        pred_tbl <- tibble(
            index   = idx,
            value   = (pred_out * scale_history + center_history)^2
        )
        
        # Combine actual data with predictions
        tbl_1 <- df %>%
            add_column(key = "actual")

        tbl_3 <- pred_tbl %>%
            add_column(key = "predict")

        # Create time_bind_rows() to solve dplyr issue
        time_bind_rows <- function(data_1, data_2, index) {
            index_expr <- enquo(index)
            bind_rows(data_1, data_2) %>%
                as_tbl_time(index = !! index_expr)
        }

        ret <- list(tbl_1, tbl_3) %>%
            reduce(time_bind_rows, index = index) %>%
            arrange(key, index) %>%
            mutate(key = as_factor(key))

        return(ret)
        
    }
    
    safe_lstm <- possibly(lstm_prediction, otherwise = NA)
    
    safe_lstm(data, epochs, ...)
    
}
```
* Next, run predict_keras_lstm_future() on the sun_spots data set.
```{r}
future_sun_spots_tbl <- predict_keras_lstm_future(sun_spots, epochs = 300)
```
* Last, we can visualize the forecast with the plot_prediction() function, setting id = NULL. We can use filter_time() to zoom in on the dataset since 1900.
```{r}
future_sun_spots_tbl %>%
    filter_time("1900" ~ "end") %>%
    plot_prediction(id = NULL, alpha = 0.4, size = 1.5) +
    theme(legend.position = "bottom") +
    ggtitle("Sunspots: Ten Year Forecast", subtitle = "Forecast Horizon: 2013 - 2023")
```
* not sure the cross validation methods introduced here is suitable for the LSMT model which is aimed at the 'long' and 'short' memories without 'breaks', which is 'splitted' in this examples. But overall the author's ideas are impressive and explorative, worth thinking !
