---
title: "Chapter 11 Intermediate portfolio analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### 11.1 Modern portfolio theory
```{r}
library(PortfolioAnalytics)
data(edhec)
data <- edhec[, 1:8]
```
#### Mean - standard deviation example - setup
```{r}
# specification
port_spec <- portfolio.spec(colnames(data))

port_spec <- add.constraint(portfolio = port_spec,
                            type = "full_investment")
port_spec <- add.constraint(portfolio = port_spec,
                            type = "long_only")
port_spec <- add.constraint(portfolio = port_spec,
                            type = "full_investment")
port_spec <- add.objective(portfolio = port_spec,
                            type = "return",
                            name = "mean")
port_spec <- add.objective(portfolio = port_spec,
                            type = "risk",
                            name = "StdDev")

print(port_spec)
```

#### Mean - standard deviation example - optimize
```{r}
# run optimization and chart results in risk-reward space
opt <- optimize.portfolio(data, portfolio = port_spec,
                          optimize_method = "random",
                          trace = TRUE)

chart.RiskReward(opt, risk.col = "StdDev",
                 return.col = "mean",
                 chart.assets = TRUE)
```

#### challenges of portfolio optimization
* Quadratic programming solver
```{r}
# load quadprog
library(quadprog)
data(edhec)
dat <- edhec[, 1:4]
```
```{r}
# constraint matrix
Amat <- cbind(1, diag(ncol(dat)), -diag(ncol(dat)))

# constriant vector
bvec <- c(1, rep(0, ncol(dat)), -rep(1, ncol(dat)))

# objective matrix
Dmat <- 10 * cov(dat)

# objective vector
dvec <- colMeans(dat)

# number of equality constraints
meq <- 1

# solve the opt problem
opt <- solve.QP(Dmat, dvec, Amat, bvec, meq)
```
```{r}
print(opt)
```
### 11.2 Portfolio spec, constraints, objectives
* work flow - spec
```{r}
# vector of assets
portfolio.spec(assets = c("SP500,", "DJIA", "Nasdaq",
                          "FTSE100", "DAX", "CAC40"))
```
```{r}
# named vector of assets with weights
initial_weights <- c("SP500" = 0.5, "FTSE100" = 0.3, "NIKKEI" = 0.2)

portfolio.spec(assets = initial_weights)
```
```{r}
# scalar of number of assets
portfolio.spec(assets = 4)
```

* workflow - add constraints
```{r}
# initialize portfolio specs
p <- portfolio.spec(assets = 4)

# add full investment constraint
p <- add.constraint(portfolio = p, type = "weight_sum",
                    min_sum = 1, max_sum = 1)

# add box constraint
p <- add.constraint(portfolio = p, type = "box",
                    min = 0.2, max = 0.6)
```

* workflow - add objectives
```{r}
p <- add.objective(portfolio = p, type = "return",
                   name = "mean")

p <- add.objective(portfolio = p, type = "risk", name = "ES",
                   arguments = list(p = 0.9, method = "gaussian"))
```
#### running optimization
```{r}
ret <- edhec[, 1:6]
head(ret, n = 3)
```
```{r}
# specification
p <- portfolio.spec(colnames(ret))

p <- add.constraint(portfolio = p,
                            type = "full_investment")
p <- add.constraint(portfolio = p,
                            type = "long_only")
p <- add.constraint(portfolio = p,
                            type = "full_investment")

p <- add.objective(portfolio = p,
                            type = "risk",
                            name = "StdDev")

```
```{r}
# optimization
opt_single <- optimize.portfolio(R = ret, 
                                 portfolio = p,
                                 optimize_method = "ROI")

opt_rebal <- optimize.portfolio.rebalancing(R = ret,
                                            portfolio = p,
                                            optimize_method = "ROI",
                                            rebalance_on = "years",
                                            training_period = 60,
                                            rolling_window = 60)
```

* workflow - analyze results
```{r}
extractWeights(opt_single)
```
```{r}
chart.Weights(opt_single)
```
```{r}
chart.Weights(opt_rebal)
```
```{r}
extractObjectiveMeasures(opt_single)
```
```{r}
head(extractObjectiveMeasures(opt_rebal))
```
* workflow - optimization analysis
```{r}
rr <- Return.portfolio(ret, weights = extractWeights(opt_rebal))
charts.PerformanceSummary(rr)
```

### 11.3 Moments
```{r}

```

