---
title: "Chapter 11 Intermediate portfolio analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### 11.1 Modern portfolio theory
```{r}
library(PortfolioAnalytics)
data(edhec)
data <- edhec[, 1:8]
```
#### Mean - standard deviation example - setup
```{r}
# specification
port_spec <- portfolio.spec(colnames(data))

port_spec <- add.constraint(portfolio = port_spec,
                            type = "full_investment")
port_spec <- add.constraint(portfolio = port_spec,
                            type = "long_only")
port_spec <- add.constraint(portfolio = port_spec,
                            type = "full_investment")
port_spec <- add.objective(portfolio = port_spec,
                            type = "return",
                            name = "mean")
port_spec <- add.objective(portfolio = port_spec,
                            type = "risk",
                            name = "StdDev")

print(port_spec)
```

#### Mean - standard deviation example - optimize
```{r}
# run optimization and chart results in risk-reward space
opt <- optimize.portfolio(data, portfolio = port_spec,
                          optimize_method = "random",
                          trace = TRUE)

chart.RiskReward(opt, risk.col = "StdDev",
                 return.col = "mean",
                 chart.assets = TRUE)
```

#### challenges of portfolio optimization
* Quadratic programming solver
```{r}
# load quadprog
library(quadprog)
data(edhec)
dat <- edhec[, 1:4]
```
```{r}
# constraint matrix
Amat <- cbind(1, diag(ncol(dat)), -diag(ncol(dat)))

# constriant vector
bvec <- c(1, rep(0, ncol(dat)), -rep(1, ncol(dat)))

# objective matrix
Dmat <- 10 * cov(dat)

# objective vector
dvec <- colMeans(dat)

# number of equality constraints
meq <- 1

# solve the opt problem
opt <- solve.QP(Dmat, dvec, Amat, bvec, meq)
```
```{r}
print(opt)
```
### 11.2 Portfolio spec, constraints, objectives
* work flow - spec
```{r}
# vector of assets
portfolio.spec(assets = c("SP500,", "DJIA", "Nasdaq",
                          "FTSE100", "DAX", "CAC40"))
```
```{r}
# named vector of assets with weights
initial_weights <- c("SP500" = 0.5, "FTSE100" = 0.3, "NIKKEI" = 0.2)

portfolio.spec(assets = initial_weights)
```
```{r}
# scalar of number of assets
portfolio.spec(assets = 4)
```

* workflow - add constraints
```{r}
# initialize portfolio specs
p <- portfolio.spec(assets = 4)

# add full investment constraint
p <- add.constraint(portfolio = p, type = "weight_sum",
                    min_sum = 1, max_sum = 1)

# add box constraint
p <- add.constraint(portfolio = p, type = "box",
                    min = 0.2, max = 0.6)
```

* workflow - add objectives
```{r}
p <- add.objective(portfolio = p, type = "return",
                   name = "mean")

p <- add.objective(portfolio = p, type = "risk", name = "ES",
                   arguments = list(p = 0.9, method = "gaussian"))
```
#### running optimization
```{r}
ret <- edhec[, 1:6]
head(ret, n = 3)
```
```{r}
# specification
p <- portfolio.spec(colnames(ret))

p <- add.constraint(portfolio = p,
                            type = "full_investment")
p <- add.constraint(portfolio = p,
                            type = "long_only")

p <- add.objective(portfolio = p,
                            type = "risk",
                            name = "StdDev")

```
```{r}
# optimization
opt_single <- optimize.portfolio(R = ret, 
                                 portfolio = p,
                                 optimize_method = "ROI")

opt_rebal <- optimize.portfolio.rebalancing(R = ret,
                                            portfolio = p,
                                            optimize_method = "ROI",
                                            rebalance_on = "years",
                                            training_period = 60,
                                            rolling_window = 60)
```

* workflow - analyze results
```{r}
extractWeights(opt_single)
```
```{r}
chart.Weights(opt_single)
```
```{r}
chart.Weights(opt_rebal)
```
```{r}
extractObjectiveMeasures(opt_single)
```
```{r}
head(extractObjectiveMeasures(opt_rebal))
```
* workflow - optimization analysis
```{r}
rr <- Return.portfolio(ret, weights = extractWeights(opt_rebal))
charts.PerformanceSummary(rr)
```

### 11.3 Moments
```{r}
# custom moment function
library(MASS)
data(edhec)
asset_returns <- edhec[,1:4]
port_spec <- portfolio.spec(assets = colnames(asset_returns))
port_spec <- add.constraint(portfolio = port_spec,
                            type = "full_investment")
port_spec <- add.constraint(portfolio = port_spec, 
                                  type = "long_only")
port_spec <- add.objective(portfolio = port_spec,
                           type = "risk",
                           name = "StdDev")

custom_fun <- function(R, portfolio, rob_method = "mcd"){
  out <- list()
  out$sigma <- cov.rob(R, method = rob_method)
  return(out)
}

# passing rod_method argument to custom fun
optimize.portfolio(R = asset_returns, portfolio = port_spec, momentFUN = custom_fun,
                   rob_method = "mcd")

optimize.portfolio(R = asset_returns, portfolio = port_spec, momentFUN = custom_fun,
                   rob_method = "mve")
```
```{r}
# custom objective function

```

### 11.4 Examples
* Benchmark
```{r}
data("indexes")
returns <- indexes[, 1:4]
```
```{r}
# equal weight benchmark
n <- ncol(returns)
equal_weights <- rep(1 / n, n)
benchmark_returns <- Return.portfolio(R = returns,
                                      weights = equal_weights,
                                      rebalance_on = "years")

colnames(benchmark_returns) <- "benchmark"
```
```{r}
# benchmark performance
table.AnnualizedReturns(benchmark_returns)
```
* Base portfolio definition
```{r}
base_port_spec <- portfolio.spec(assets = colnames(returns))
base_port_spec <- add.constraint(portfolio = base_port_spec,
                             type = "full_investment")
base_port_spec <- add.constraint(portfolio = base_port_spec,
                                 type = "long_only")
base_port_spec <- add.objective(portfolio = base_port_spec,
                                type = "risk",
                                name = "StdDev")
```

* optimization backtest
```{r}
opt_base <- optimize.portfolio.rebalancing(R = returns,
                                           optimize_method = "ROI",
                                           portfolio = base_port_spec,
                                           rebalance_on = "quarters",
                                           training_period = 60,
                                           rolling_window = 60
                                           )

# calculate portfolio returns
base_returns <- Return.portfolio(returns,
                                 extractWeights(opt_base))

colnames(base_returns) <- "base"
```
* optimization backtest
```{r}
# chart the optimal weights
chart.Weights(opt_base)
```
```{r}
# merge benmark and portfolio returns
ret <- cbind(benchmark_returns, base_returns)

# annualized performance
table.AnnualizedReturns(ret)

```

* refine constraints
```{r}
# backup of portfolio spec
box_port_spec <- base_port_spec

# update the constraint
box_port_spec <- add.constraint(portfolio = box_port_spec,
                                type = "box",
                                min = 0.05,
                                max = 0.4,
                                indexnum = 2)
```

```{r}
# backtesting
opt_box <- optimize.portfolio.rebalancing(R = returns,
                                          optimize_method = "ROI",
                                          portfolio = box_port_spec,
                                          rebalance_on = "quarters",
                                          training_period = 60,
                                          rolling_window = 60)
# calculate portfolio returns
box_returns <- Return.portfolio(returns, extractWeights(opt_box))
colnames(box_returns) <- "box"

```
```{r}
# chart the optimal weights
chart.Weights(opt_box)
```

* analysis refined constraints
```{r}
# merge box port returns
ret <- cbind(ret, box_returns)

# annualized performance
table.AnnualizedReturns(ret)
```
* no improvement using 'box' ?
