---
title: "Chapter 01 Fundamentals of Automated Trading"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Equity Curve and Return Series
## Risk-Return Metrics
## Characteristics of Risk-Return Metrics
### Listing 1-1. Loading SPY Data
```{r}
# Checks if quantmod is installed, installs it if unavailable,
# loads it and turns off needless warning messages
if(!("quantmod" %in% as.character(installed.packages()[,1])))
  { install.packages("quantmod") } 
library(quantmod)
options("getSymbols.warning4.0"=FALSE, 
        "getSymbols.auto.assign"=FALSE)

# Loads S&P 500 ETF data, stores closing prices as a vector
SPY <- suppressWarnings(
  getSymbols(c("SPY"),from = "2012-01-01"))
SPY <- as.numeric(SPY$SPY.Close)[1:987]
```
### Listing 1-2. Simulating Equity Curves
```{r}
# Set Random Seed
set.seed(123)

# Create Time Index
t <- 1:(length(SPY)-1)
 
# Tradable Capital Vector
Vt <- c(rep(10000, length(t)))

# Benchmark Return Series
Rb <- rep(NA, length(t))
for(i in 2:length(t)) { Rb[i] <- (SPY[i] / SPY[i - 1]) - 1 }

# Benchmark Equity Curve
Eb <- rep(NA, length(t))
Eb[1] <- Vt[1]
for(i in 2:length(t)) { Eb[i] <- Eb[i-1] * (1 + Rb[i]) }

# Randomly Simulated Return Series 1
Rt <- rep(NA, length(t))
for(i in 2:length(t)){
  Rt[i] <- Rb[i] + rnorm(n = 1,
                         mean = 0.24/length(t),
                         sd = 2.5 * sd(Rb, na.rm = TRUE))
} 

# Randomly Simulated Return Series 2
Rt2 <- rep(NA, length(t))
for(i in 2:length(t)){
  Rt2[i] <- Rb[i] + rnorm(n = 1,
                         mean = 0.02/length(t),
                         sd = .75 * sd(Rb, na.rm = TRUE))
} 

# Randomly Simulated Equity Curve 1
Et <- rep(NA, length(t))
Et <- Vt[1]
for(i in 2:length(t)) { Et[i] <- Et[i-1] * (1 + Rt[i]) }

# Randomly Simulated Equity Curve 2
Et2 <- rep(NA, length(t))
Et2 <- Vt[1]
for(i in 2:length(t)) { Et2[i] <- Et2[i-1] * (1 + Rt2[i]) }
```

### Plot Et1 against SPY portifolio
```{r}
# Plot of Et1 against the SPY Portfolio
plot(y = Et, x = t, type = "l", col = 1,
     xlab = "Time",
     ylab= "Equity ($)",
     main = "Figure 1.3: Randomly Generated Equity Curves")
grid()
abline(h = 10000)
lines(y = Et2, x = t, col = 2)
lines(y = Eb, x = t, col = 8)
legend(x = "topleft", col = c(1,2,8), lwd = 2, legend = c("Curve 1",
                                                          "Curve 2",
                                                          "SPY"))
```

## Sharpe Ratio
### Listing 1-3. High-Frequency Sharpe Ratio
```{r}
# Use na.rm = TRUE to ignore NA's at position 1 in return series
SR <- mean(Rt, na.rm = TRUE) / sd(Rt, na.rm = TRUE)
SR2 <- mean(Rt2, na.rm = TRUE) / sd(Rt2, na.rm = TRUE) 
SRb <- mean(Rb, na.rm = TRUE) / sd(Rb, na.rm = TRUE)
```
### Listing 1-4. Plotting Equity Curve Against Performance Metrics
```{r}
plot(y = Et, x = t, type = "l", col = 1,
     xlab = "",
     ylab= "Equity ($)",
     main = "Figure 1.4: Sharpe Ratios")
grid()  
abline(h = 10000)
lines(y = Et2, x = t, col = 2)
lines(y = Eb, x = t, col = 8)
legend(x = "topleft", col = c(1,2,8), lwd = 2,
       legend = c(paste0("SR = ", round(SR, 3)),
                  paste0("SR = ", round(SR2, 3)),
                  paste0("SR = ", round(SRb, 3))))
```

## Maximum Drawdown Ratios
### Listing 1-5. Maximum Drawdown Function
```{r}
MD <- function(curve, n = 1){
  
  time <- length(curve) 
  v <- rep(NA, (time * (time - 1)) / 2)
  k <- 1
  for(i in 1:(length(curve)-1)){
    for(j in (i+1):length(curve)){
      v[k] <- curve[i] - curve[j]
      k <- k + 1
    }
  }
  
  m <- rep(NA, length(n))
  for(i in 1:n){
    m[i] <- max(v)
    v[which.max(v)] <- -Inf
  }
  
  return(m)
  
}
```
### Listing 1-6. Maximum Drawdown Ratios
```{r}
NPMD <- (Et[length(Et)] - Vt[1]) / MD(Et)

Burke <- (Et[length(Et)] - Vt[1]) /
          sqrt((1/length(Et)) * sum(MD(Et, n = round(length(Et) / 20))^2))
```
## Partial Moment Ratios
### Listing 1-7. Partial Moment Function
```{r}
PM <- function(Rt, upper = FALSE, n = 2, Rb = 0){
  if(n != 0){
    if(!upper) return(mean(pmax(Rb - Rt, 0, na.rm = TRUE)^n))
    if(upper) return(mean(pmax(Rt - Rb, 0, na.rm = TRUE)^n))
  } else {
    if(!upper) return(mean(Rb >= Rt))
    if(upper) return(mean(Rt > Rb))
  }
}
```
### Listing 1-8. Partial Moment Ratios
```{r}
Omega <-  mean(Rt, na.rm = TRUE) / PM(Rt)^0.5
UPR <- PM(Rt, upper = TRUE)^0.5 / PM(Rt)^0.5
```
## Regression-Based Performance Metrics
### Listing 1-9. Regression Against Benchmark
```{r}
# Scatterplot of Rt against Rb
plot(y = Rt, x = Rb,
pch = 20,
cex = 0.5,
xlab = "SPY Returns",
ylab= "Return Series 1",
main = "Figure 1-7: Return Series 1 vs. SPY")
grid()
abline(h = 0)
abline(v = 0)

# Compute and store the regression model
model <- lm(Rt ~ Rb)

# Plot the regression line
abline(model, col = 2)

# Display alpha and beta
legend(x = "topleft", col = c(0,2), lwd = 2,
       legend = c("Alpha   Beta   R^2",
                  paste0(round(model$coefficients[1], 4), "   ",
                         round(model$coefficients[2], 2), "   ",
                         round(summary(model)$r.squared, 2))))
```

```{r}
# Create linearized equity curve and run regression
y <- Et / Vt
model <- lm(y ~ t)

# Compute PPS by pulling "r.squared" value from summary function
PPS <- ((Et[length(Et)] - Vt[1]) / Vt[1]) * summary(model)$r.squared
```

